Understanding Traffic Patterns and Median Speeds: Insights from Toronto’s Speed Display Program

### 2024-12-01 paper/paper.qmd
rendered paper

$$
\begin{gathered}
y_i \mid \mu_i, \sigma \sim \operatorname{Normal}\left(\mu_i, \sigma\right) \\
\mu_i=\alpha+\beta_1 x_{1 i}+\gamma_1 \mathrm{NB}_i+\gamma_2 \mathrm{SB}_i+\gamma_3 \mathrm{WB}_i \\
\alpha \sim \operatorname{Normal}(0,2.5) \\
\beta_1 \sim \operatorname{Normal}(0,2.5) \\
\gamma_1, \gamma_2, \gamma_3 \sim \operatorname{Normal}(0,2.5) \\
\sigma \sim \operatorname{Exponential}(1)
\end{gathered}
$$

@@

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

plot(first_model, "trace")

plot(first_model, "rhat")
```

>>>>

$$
\begin{aligned}
y_i \mid \mu_i, \sigma \sim \operatorname{Normal}\left(\mu_i, \sigma\right) \\
\mu_i=\alpha+\beta_1 x_{1 i}+\gamma_1 \mathrm{NB}_i+\gamma_2 \mathrm{SB}_i+\gamma_3 \mathrm{WB}_i \\
\alpha \sim \operatorname{Normal}(0,2.5) \\
\beta_1 \sim \operatorname{Normal}(0,2.5) \\
\gamma_1, \gamma_2, \gamma_3 \sim \operatorname{Normal}(0,2.5) \\
\sigma \sim \operatorname{Exponential}(1)
\end{aligned}
$$

@@

pp_check(Bayesian_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(Bayesian_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

plot(Bayesian_model, "trace")

plot(Bayesian_model, "rhat")
```
